Supplementary Materials

### 2020-05-29 analysis/analysis.Rmd
Removing undeeded comparisons and more table colouring
added graphical representation of symmetries in each group

## Subgroup Information

Import subgroup information and display a table of the relationships that we will be investigating.

@@

>>>>

## Symmetry Information

### Subgroup Relationships
Import subgroup information and display a table of the relationships that we will be investigating.

@@

### Types of Symmetry

```{r, fig.cap = "Symmetries present in each group"}
sym_dat <- read_csv("../subgroups/symmeries_in_group.csv") %>%
  mutate(group = str_to_upper(group))

sym_dat %>% pivot_longer(-group, names_to = "symmetry", values_to = "order") %>%
  ggplot(aes(x = symmetry, y = order, fill = as.factor(order))) + geom_col() + facet_wrap(~ group) +
  theme_bw() + 
  scale_y_continuous(breaks = c(2,4,6)) + 
  ggthemes::scale_fill_ptol() + 
  theme(
    panel.grid.minor=element_blank(), 
    legend.position = "none")
